### 2016-07-04 case-studies.tex
edits

\paragraph{Microblog.} Our second set of experiments focused on a
Twitter-like microblogging application taken from~\cite{railsbook}.
An important invariant that must be preserved is the referential
integrity between microposts and authors. The application enforces
this invariant entirely in user space by relying on database-backed
transactions (this behavior is typical of Rails
applications~\cite{bailisferal}).  For instance, deletion of a user is
carried out in a transaction that also includes the deletion of
microposts authored by the user.  However, it is possible for
concurrent observers to nonetheless witness invariant violations. To
measure the likelihood of such anomalies, we first populated a
Postgres database with 1000 user accounts, each user with 50
microposts and 20 followers, chosen uniformly at random. We then
constructed experiments with 64 concurrent clients performing
deletions and timeline reads of randomly chosen users in a 1:7 ratio,
and witnessed 250 violations of referential integrity (the isolation
level was left at the default {\sc rc} level for experiments). To
determine appropriate isolation levels, we then instantiated our
framework for an {\sc sc} store with various ANSI SQL isolation levels
for user deletions and timeline reads, and obtained a proof that {\sc
rc} is sufficient for deletions, whereas reads require {\sc rr}. The
proof is immediately applicable for MySQL, which implements ANSI SQL
isolation levels. Repeating our experiments for MySQL with this
configuration resulted in no violations (as expected), while yielding
a 38\% reduction in latency than an {\sc ser} configuration.  Since
Postgres's isolation levels are stronger than the corresponding ANSI
levels, \rulelabel{RG-Conseq} rule (Fig.~\ref{fig:rg-rules}) lets us
immediately deduce that the same choice of isolation levels also work
on Postgres.

>>>>

\paragraph{Microblog.} Our second set of experiments focused on a
Twitter-like microblogging application taken from~\cite{railsbook}.
An important invariant that must be preserved is the referential
integrity between microposts and authors. The application enforces
this invariant entirely in user space by relying on database-backed
transactions (this behaviour is typical of Rails
applications~\cite{bailisferal}).  For instance, deletion of a user is
carried out in a transaction that also includes the deletion of
microposts authored by the user.  However, it is possible for
concurrent observers to nonetheless witness invariant violations. To
measure the likelihood of such anomalies, we first populated a
Postgres database with 1000 user accounts, each user with 50
microposts and 20 followers, chosen uniformly at random. We then
constructed experiments with 64 concurrent clients performing
deletions and timeline reads of randomly chosen users in a 1:7 ratio,
and witnessed 250 violations of referential integrity (the isolation
level was left at the default {\sc rc} level for experiments). To
determine appropriate isolation levels, we then instantiated our
framework for an {\sc sc} store with various ANSI SQL isolation levels
for user deletions and timeline reads, and obtained a proof that {\sc
rc} is sufficient for deletions, whereas reads require {\sc rr}. The
proof is immediately applicable for MySQL, which implements ANSI SQL
isolation levels. Repeating our experiments for MySQL with this
configuration resulted in no violations (as expected), while yielding
a 38\% reduction in latency than an {\sc ser} configuration.  Since
Postgres's isolation levels are stronger than the corresponding ANSI
levels, \rulelabel{RG-Conseq} rule (Fig.~\ref{fig:rg-rules}) lets us
immediately deduce that the same choice of isolation levels also work
on Postgres.
